Capturing Policies for BYOD

### 2016-10-25 paper.tex
describes types

We have used AppPAL to formalise the BYOD policies.
AppPAL is an instantiation of Becker's SecPAL~\cite{becker_secpal:_2010} we have previously used to describe app privacy preferences~\cite{hallett_apppal_2016}.
To describe BYOD policies we have extended AppPAL with types.
This allows our policies to be more succinct and readable whilst losing none of the expressive power.
When describing variables in the head of an AppPAL assertion.

>>>>

When using AppPAL to describe policies, we need to describe what domain each variable belongs to.
AppPAL inherits from SecPAL (and Datalog) a safety condition that all variables in the head of an assertion must be referenced in the body.
This leads to policies which can be noisy to read.
For example in the SANS policy there is a rule that states that devices can only connect to wireless access points owned by the company.
This is written in AppPAL as:
\begin{lstlisting}
'company' says Device canConnectToAP(AP)
  if AP isOwnedByCompany,
     Device isDevice,
     AP isAccessPoint.
\end{lstlisting}
To simplify the presentation we allow a special sugared notation for conditionals expressing the type of a variable (\emph{variable \emph{is}Type}).
Any variable in the head of the rule of the form \texttt{\emph{Type}:Variable} is replaced by the variable and a conditional that \textt{Variable is\emph{Type}} is added to the body.
The rule can be re-written as shown bellow hiding the typing statements.
\begin{lstlisting}
'company' says Device:D canConnectToAP(AP:X)
  if X isOwnedByCompany.
\end{lstlisting}
